Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-08-03 output/latex/manuscript.tex
add addresses and countries for all authors

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA, USA.
\textsuperscript{5} Vanderbilt University Medical Center.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, New York, USA.
\textsuperscript{8} Mayo Clinic.
\textsuperscript{9} Northwestern University.
\textsuperscript{10} Kahlert School of Computing, University of Utah, Salt Lake City, UT, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.

>>>>

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA 94305, USA.
\textsuperscript{5} Vanderbilt University Medical Center, Nashville, TN 37232, USA.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center, Cincinnati, OH 45229, USA.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, NY 10032, USA.
\textsuperscript{8} Mayo Clinic, Rochester, MN 55905, USA.
\textsuperscript{9} Northwestern University, Chicago, IL 60611, USA.
\textsuperscript{10} Kahlert School of Computing, University of Utah, Salt Lake City, UT 84112, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.
